Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-15 paper/main.tex
QA on conclusion and appendix

\section{Tahoe-LAFS}
%What is it, how/where are hash functions used, Python, pycryptopp
%comparison with RAID-6, mutable/immutable?

@@

A hash of the encryption key is used to form the "storage index", which is
used for both server selection and to index shares within each storage node.
% More here?

@@

%A bit more technical description of how we tested the candidates in Tahoe-LAFS
% - Limitations/assumptions
% - Optimized candidates.
% - Error sources.
% The points above should be taken into consideration on each section in this
% chapter.

@@

% Describe inconsistencies in the numbers, and try to explain them.
% Time spent not hashing varies because: Variable use of CPU regs?
%
% Compare our results with general (SUPERCOP) results.
%
% How much gain can Tahoe-LAFS get by switching to SHA-3?

@@

% This chapter should contain:
% -----------------------------------------------------------
% A somewhat short conclusion summing up what has been done, and results and
% discussion

We had hoped to contribute more to the Open Source project Tahoe-LAFS, when
starting on our assignment. It was early evident that implementing a new
capability was out of scope, since creating Python bindings and trying out
new implementations was prioritized. Future work should implement the support
for choosing hashing algorithm in a proper manner which ensures backwards
compatibility.

Four of the candidates has been shown to perform better than the currently used
SHA-256 -- BLAKE, BlueMidnightWish, Shabal and Simd. The time it takes for
Tahoe-LAFS to upload a one gigabyte file, could improve by $5\%$ if the best
performing SHA-3 candidate, BLAKE, were to be used. One has to bear in mind that
SHA-256 has been optimized and tweaked for a number of years, and that these
performance differences undoubtedly will continue to increase as new and better
implementations will be developed for the final chosen \ac{SHA}-3 algorithm.

Perhaps the most important finding in this project, is that the SUPERCOP
benchmarking indeed drives the development of new and better implementations
forward, but since the SUPERCOP \ac{API} does not conform to the \ac{NIST}
\ac{API}, the developers leave important functionality out (i.e.
{\verb update() }), and hence make it difficult for people who wish to try out
and test the \ac{SHA}-3 candidates in real world applications.

@@

% Uncomment to enable appendices.
\appendix
\appendixpage
\addappheadtotoc

@@

Tables \ref{tbl:tahoe:optimized_g} and \ref{tbl:tahoe:optimized_p} exhibit
results calculated which theoretically could have been achieved using the best
\ac{SUPERCOP} implementation for each candidate in Tahoe-\ac{LAFS}. The
calculations uses medians from \autoref{app:supercop:bench} for the speed
of each candidate, the exact sizes for each call to the hash function from
\autoref{sec:results:tahoedata}, and interpolation to estimate the time to
hash a length not recorded by \ac{SUPERCOP}. For lengths above 4096B, the
numbers for long data lengths are used. The results also assume only one core
of the reference processor (2,833 GHz) is used. We can see that some of the calculations,
e.g. for Shavite3 are worse than the result we achieved in our measurements,
this is probably due to interpolation being an inaccurate method to use for
the shorter lengths of data.

>>>>

\section{Tahoe-LAFS}

@@

A hash of the encryption key is used to form the "storage index", which is
used for both server selection and to index shares within each storage node.

@@

@@

@@

We had hoped to contribute more to the Open Source project Tahoe-\ac{LAFS}, when
starting on our assignment. It was early evident that implementing a new
capability was out of scope, since creating Python bindings and trying out
new implementations were prioritized. Future work should implement the support
for choosing hashing algorithm in a proper manner, which ensures backwards
compatibility.

Four of the candidates have been shown to perform better than the currently used
SHA-256 -- BLAKE, BlueMidnightWish, Shabal and Simd. The time it takes for
Tahoe-\ac{LAFS} to upload a one gigabyte file, could improve by $5\%$ if the
best performing \ac{SHA}-3 candidate, BLAKE, were to be used. One has to bear in
mind that \ac{SHA}-256 has been optimized and tweaked for a number of years, and
that these performance differences undoubtedly will continue to increase as new
and better implementations will be developed for the final chosen \ac{SHA}-3
algorithm.

Perhaps the most important finding in this project, is that the \ac{SUPERCOP}
benchmarking indeed drives the development of new and better implementations
forward, but since the \ac{SUPERCOP} \ac{API} does not conform to the \ac{NIST}
\ac{API}, the developers leave important functionality out (i.e.
{\verb update() }), and hence make it difficult for people who wish to try out
and test the \ac{SHA}-3 candidates in real world applications.

@@

\appendix
\appendixpage
\addappheadtotoc

@@

Tables \ref{tbl:tahoe:optimized_g} and \ref{tbl:tahoe:optimized_p} exhibit
results calculated, which theoretically could have been achieved using the best
\ac{SUPERCOP} implementation for each candidate in Tahoe-\ac{LAFS}. The
calculations uses medians from \autoref{app:supercop:bench} for the speed of
each candidate, the exact sizes for each call to the hash function from
\autoref{sec:results:tahoedata}, and interpolation to estimate the time to hash
a length not recorded by \ac{SUPERCOP}. For lengths above 4096B, the numbers for
long data lengths are used. The results also assume only one core of the
reference processor (2,833 GHz) is used. We can see that some of the
calculations, e.g. for Shavite3, are worse than the result we achieved in our
measurements, this is probably due to interpolation being an inaccurate method
to use for the shorter lengths of data.
